Error Reporting Parsers: a Monad Transformer Approach

### 2013-05-16 article.tex
bibliography:  add references, cite them, create simple build script to run pdflatex and bibtex

\begin{introduction}
Parsing is "the process of analysing a string of symbols according to the rules
of a formal grammar" (Wikipedia), with the general goal of building a tree
representing the structure of the parsed input, upon which further operations
such as interpretation or code generation are then performed.

@@

@@

\section{Monad transformers}
Monad transformers allow monads to be modularly combined to form new monads
which combine the semantics of their constituents.  That's exactly what we need
to do to build parsers.
We'll try to use the standard transformers/mtl libraries as much as possible, 
since they're easy to obtain, easy to use, and quite effective in practice, but
occasionally we'll have to make an extension to avoid certain type class
instances.

@@

The language definition in pseudo-BNF is:

@@

\section{Stack Order}
Not only are the contents of a transformer stack important, but the order of the
layers as well.  Let's revisit our first woof parser -- what if our stack had
instead been Maybe/State instead of State/Maybe?
\begin{verbatim}
State/Maybe:   s -> Maybe (a, s)

@@

\bibliography{Author}

>>>>

\begin{introduction}
Parsing is "the process of analysing a string of symbols according to the rules
of a formal grammar" \cite{wikipedia_parsing}, with the general goal of building a tree
representing the structure of the parsed input, upon which further operations
such as interpretation or code generation are then performed.

@@

There are such many excellent papers for reading about parser combinators, such
as this \cite{wadler}, this \cite{hutton}, and this \cite{leijen}.  In fact, the
inspiration and terminology for much of this article is drawn directly from
those references.

@@

\section{Monad transformers}
Monad transformers \cite{liang} allow monads to be modularly combined to form new monads
which combine the semantics of their constituents.  That's exactly what we need
to do to build parsers.
We'll try to use the standard transformers/mtl \cite{mtl} libraries as much as possible, 
since they're easy to obtain, easy to use, and quite effective in practice, but
occasionally we'll have to make an extension to avoid certain type class
instances.

@@

The language definition in pseudo-BNF \cite{bnf} is:

@@

\section{Stack Order}
Not only are the contents of a transformer stack important, but the order of the
layers as well \cite{stack}.  Let's revisit our first woof parser -- what if our stack had
instead been Maybe/State instead of State/Maybe?
\begin{verbatim}
State/Maybe:   s -> Maybe (a, s)

@@

\bibliography{article}
